%-------------------------------------------------------------------------------
\section{Goals}
\label{s:goals}
%-------------------------------------------------------------------------------


Developers use the different quality of service (QOS) classes that Kubernetes
supports to run different services with different latency needs. We expect a
multi-tenant setting, where developers have to pay for the resources they use.

The highest QOS class is Guaranteed. Guaranteed services are guaranteed access
to the number of CPUs they request, but are also limited to them. Developers
using this class ned to provision and thus pay for peak load, and in return get
guaranteed access to enough resources to handle peak load. Examples include
critical infrastructure like databases~\cite{reddit-kub-qos}.

The middle QOS class is Burstable. Burstable services are similarly guaranteed
access to the number of CPUs they requested, but are also allowed to use CPUs
beyond their reservation opportunistically. This is the category in which a web
server would be expected to run, where it can make use of the bursting in
moments of higher load. As a result, developers can provision for closer to
average load. If the number of services bursting at the same time is low, each
will be able to use slack of other services to handle the bursting load.
However, it is not guaranteed that the resources will be available.

The lowest QOS class is BestEffort. BestEffort services are only allowed to run
on resources that would otherwise go idle. For instance, if a CPU has completely
run out of Burstable and Guaranteed things to run, it should run BestEffort
threads. This is the QOS class that a developer would run background data
analytics or image resize jobs, where the time to completion is inconsequential.

In Kubernetes, the reservations and limits are expressed by attaching resource
`requests' and `limits' to pods. These are expressed as a number of vCPUs, and
can be fractional (\ie{} a pod could request 0.5 vCPUs). Pods are BestEffort if
their request is 0, and are Guaranteed if they have both a request and a limit
and those two are the same.

